Stat 400 Presentation

### 2021-12-09 Stat 400 presentation.Rmd
Changed some titles
Set seed, and pdf

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width=200)
```

@@

- Step Function
  <!-- ![Sample](/cloud/project/image.jpg) -->

@@

@@

## 'Flatten the Curve' - Pseudo Vaccination Effect

>>>>

```{r setup, include=FALSE}
set.seed(400)
knitr::opts_chunk$set(echo = FALSE)
options(width=200)
```

@@

- Step Function
![Sample](/cloud/project/image.jpg)

@@

## Plot With Bootstrap 95% CI, 200 subjects

@@

## Pseudo Vaccination Effect
